% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass{exam} % use larger type; default would be 10pt

%%% END Article customizations

%%% The "real" document content comes below...

\usepackage{syntax}

\newcommand{\spacedQuestion}[2][1] {
  \question
  {#2}
  \vspace{\stretch{#1}}
}

\begin{document}

\begin{questions}

  \spacedQuestion {
    Why do we study programming languages? (Give three reasons)
  }


  \spacedQuestion {
    One day your project manager decides that every new program your team produces is to be written in machine language, since computers don't understand C++ anyway. Other than referring them to a therapist, what are some things you could tell them to alleviate the situation?
  }

  \spacedQuestion { Define programming language: }

  \spacedQuestion { What is the fetch-execute cycle? }

  \spacedQuestion { What was the first high level language? }

  \spacedQuestion { Who invented Fortran? }

  \spacedQuestion { When was Fortran invented? }

  \spacedQuestion { What is the only high level structure in Fortran? }

  \spacedQuestion { What was the purpose of the do-loop with regards to efficiency? }

  \spacedQuestion { Define a compiler }

  \pagebreak

  \spacedQuestion Define an Interpreter:

  \spacedQuestion How does a compiler differ from an interpreter?

  \spacedQuestion What did the loader do in the first assignment (psuedo-code interpreter)?

  \spacedQuestion Explain how psuedo-code interpreters are related to virtual computers.

  \spacedQuestion How many IO statements did Fortran have?

  \spacedQuestion How was floating point calculation handled in the earliest computer systems?

  \spacedQuestion Name each advance related to the IBM 704 as discussed in class.

  \spacedQuestion How were Fortran subprograms compiled with respect to the entire program?

  \spacedQuestion Explain how Fortran implemented recursion.

  \spacedQuestion What is static allocation?

  \spacedQuestion Why are GOTO statements considered harmful?

  \spacedQuestion Define the Static Structure Principle

  \spacedQuestion Define the Zero, One, Infinity Principle

  \spacedQuestion Derive the Fortran 1-D addressing equation

  \spacedQuestion Derive a 2-D addressing equation from the previously derived equation.

  \spacedQuestion What is the origin of Fortran control structures?

  \pagebreak

  \spacedQuestion { FORTRAN Syntax/Semantics
  \begin{parts}
    \part Do loop
    \vspace{\stretch{1}}

    \part Arithmitic IF
    \vspace{\stretch{1}}

    \part GOTO statement
    \vspace{\stretch{1}}

    \part Common block
    \vspace{\stretch{1}}

    \part EQUIVALENCE statement
    \vspace{\stretch{1}}
  \end{parts}
  }
  \pagebreak

  \spacedQuestion ALGOL Statistics
  \begin{parts}
    \part Year?
    \vspace{\stretch{1}}
    \part Who invented it?
    \vspace{\stretch{1}}
    \part Name three objectives/goals for the newly created ALGOL.
    \vspace{\stretch{1}}
    \part Explain the main difference between ALGOL-60 and ALGOL-58.
    \vspace{\stretch{1}}
    \part Practically nobody wrote programs for ALGOL and its definitly not used today. Why is it such a big deal?
    \vspace{\stretch{1}}
    \part Why did nobody write programs for ALGOL?
  \end{parts}
  \pagebreak
  
  \spacedQuestion { BNF
  \begin{parts}
    \part What does BNF stand for? (hint: its not Best New Friend)
    \vspace{\stretch{1}}

    \part Who invented BNF
    \vspace{\stretch{1}}

    \part Where was it first used?
    \vspace{\stretch{1}}

    \part What is the purpose of BNF?
    \vspace{\stretch{1}}
  \end{parts}
  }
  \pagebreak

  \spacedQuestion { Define variable scope within the context of programming languages }

  \spacedQuestion { Explain the dangling-else problem. }

  \spacedQuestion {
     How long does each of the below scopes bind a variable to an address?
  \begin{parts}
    \part Global
    \vspace{\stretch{1}}

    \part Function
    \vspace{\stretch{1}}

    \part Block
    \vspace{\stretch{1}}
  \end{parts}
  }

  \spacedQuestion {
    What is the name of the area in memory that stores variables?
  }
  \vspace{\stretch{1}}

  \spacedQuestion {
    Isn't a compound statement just a fancy word for a block? Why/Why not? What is a block anyway?
  }

  \pagebreak

  \spacedQuestion {
     Define feature interaction in the context of programming languages.
  }


  \spacedQuestion {
    Name one feature interaction in FORTRAN.
  }

  \spacedQuestion {
    What is dynamic scoping?
  }

  \spacedQuestion {
    Define Grammar in the context of programming languages.
  }

  \spacedQuestion {
    How do we define a Grammar for a programming language?
  }

  \spacedQuestion {
    What is the syntax of the rewrite rule?
  }

  \spacedQuestion {Produce a parse tree for the statement `b c f d f' with the below grammar using a top down technique:
    \begin{grammar}
      <S> $\rightarrow$ b <A> <S> | <B>

      <A> $\rightarrow$ <A> <B> d | c

      <B> $\rightarrow$ f
    \end{grammar}
  }

  \spacedQuestion { Define parsing }

  \spacedQuestion { List Chomsky's four types of grammar }

  \spacedQuestion { Which types can today's programming languages parse? }

  \spacedQuestion { Draw a link list structure for the following LISP code \\ (car (cons '(a b c) (cdr (cons '(a b) '(c d))))) }

  \spacedQuestion { What would be the results of the following LISP commands? 
  \begin{parts}
    \part (cons '(too) '(be or not (to be)))
  \end{parts}
  }

  \spacedQuestion {
    What ALGOL-60 feature does Jensen's device rely on?
  }

  \spacedQuestion {
    Pascal Statistics
  \begin{parts}
    \part Year?
    \part Who invented it?
    \part What was Pascals contribution to programming languages?
  \end{parts}
  }

\end{questions}

\end{document}